%% -*- coding: utf-8 -*-
%% Timestamp: "2025-05-05 12:30:00 (ywatanabe)"
%% File: "/home/ywatanabe/proj/SciTex/manuscript/src/abstract.tex"

\begin{abstract}
  \pdfbookmark[1]{Abstract}{abstract}
  % This demonstrates how to write an effective abstract for a scientific paper
  
  Scientific manuscript preparation presents significant challenges, particularly for researchers balancing complex content with formatting requirements. This paper introduces SciTex, an AI-assisted LaTeX template system designed to streamline the document preparation workflow. SciTex integrates modular LaTeX templates with artificial intelligence tools that assist with text revision, terminology consistency, and citation management. We evaluated the system through a user study with 50 researchers across multiple disciplines, demonstrating a 45\% reduction in document preparation time compared to traditional methods. Quality assessments show that AI-revised text achieved clarity and grammar scores comparable to expert revisions while maintaining scientific accuracy. Key innovations include automated figure and table management, version control integration, and a standardized compilation pipeline. The template system is adaptable to various journal formats and includes comprehensive documentation. By reducing technical barriers to effective LaTeX usage, SciTex makes high-quality document preparation more accessible to researchers, potentially enhancing scientific communication across disciplines.
\end{abstract}

%%%% EOF