%% -*- coding: utf-8 -*-
%% Timestamp: "2025-05-04 08:33:31 (ywatanabe)"
%% File: "/home/ywatanabe/proj/SciTex/manuscript/src/additional_info.tex"
\pdfbookmark[1]{Additional Information}{additional_information}

\pdfbookmark[2]{Ethics Declarations}{ethics_declarations}                    
\section*{Ethics Declarations}
All study participants provided their written informed consent ...
\label{ethics declarations}

\pdfbookmark[2]{Contributors}{author_contributions}                    
\section*{Author Contributions}
Y.W. conceptualized the study, designed the template system, and developed the core components. Claude Code assisted with text refinement, content organization, and feature documentation. Y.W. supervised and validated all aspects of the final manuscript.
\label{author contributions}

\pdfbookmark[2]{Acknowledgments}{acknowledgments}                    
\section*{Acknowledgments}
This research was funded by ...
\label{acknowledgments}

\pdfbookmark[2]{Declaration of Interests}{declaration_of_interest}                    
\section*{Declaration of Interests}
The authors declare that they have no competing interests.
\label{declaration of interests}

\pdfbookmark[2]{Inclusion and Diversity Statement}{inclusion_and_diversity_statement}        
\section*{Inclusion and Diversity Statement}
We support inclusive, diverse, and equitable conduct of research.
\label{inclusion and diversity statement}

\pdfbookmark[2]{Declaration of Generative AI in Scientific Writing}{declaration_of_generative_ai}
\section*{Declaration of Generative AI in Scientific Writing}
The authors utilized Claude Code, provided by Anthropic, for enhancing manuscript content organization, text conciseness, and formatting consistency. The authors reviewed and verified all AI-generated content. Responsibility for the final manuscript content rests entirely with the authors.
\label{declaration of generative ai in scientific writing}

%% \pdfbookmark[2]{Appendices}{appendices}                    
%% \appendix
%% \section{}
%% \label{}

%%%% EOF