%% -*- coding: utf-8 -*-
%% Timestamp: "2025-09-26 18:19:38 (ywatanabe)"
%% File: "/ssh:sp:/home/ywatanabe/proj/neurovista/paper/01_manuscript/src/discussion_revised.tex"

\section{Discussion}

\subsection{Principal Findings}
Our comprehensive analysis of phase-amplitude coupling in long-term iEEG recordings from the NeuroVista dataset reveals several key insights into seizure dynamics and prediction. The observation of progressive PAC enhancement during the pre-ictal period, particularly in theta/alpha-gamma coupling, supports the hypothesis that seizures arise from a gradual transition in network dynamics rather than sudden, unpredictable events. This finding has important implications for the development of seizure warning systems and our understanding of epileptogenesis.

\subsection{Mechanisms of PAC in Seizure Generation}
The dominant theta-gamma PAC pattern observed in our study aligns with established theories of cortical information processing and pathological synchronization in epilepsy. Low-frequency oscillations (theta/alpha) are thought to coordinate activity across distributed neural populations, while high-frequency gamma oscillations reflect local processing and neuronal firing. The increased coupling strength during pre-ictal periods suggests a pathological enhancement of this coordination mechanism, potentially reflecting:

1. \textbf{Network hypersynchronization}: Progressive recruitment of neuronal populations into synchronized states
2. \textbf{Excitation-inhibition imbalance}: Failure of inhibitory control mechanisms leading to runaway excitation
3. \textbf{Critical state transitions}: Approach to a bifurcation point in neural dynamics

The spatial spread of PAC elevation from focal to distributed patterns mirrors the clinical evolution from focal onset to secondary generalization, providing an electrophysiological correlate of seizure propagation.

\subsection{Clinical Translation and Implementation}
The robust discrimination between interictal and pre-ictal states using PAC features (mean AUC > 0.XX) demonstrates clinical potential for seizure forecasting. Key advantages of PAC-based prediction include:

\textbf{Computational efficiency}: Our PyTorch-accelerated implementation enables real-time processing suitable for implantable devices with limited computational resources. The modulation index calculation requires only basic signal processing operations implementable in low-power hardware.

\textbf{Interpretability}: Unlike black-box machine learning approaches, PAC provides physiologically meaningful features that clinicians can interpret in the context of known seizure mechanisms.

\textbf{Stability}: The use of z-scored PAC values normalized to patient-specific baselines accounts for inter-individual variability and electrode placement differences, improving generalizability.

\subsection{Limitations and Methodological Considerations}

Several limitations should be considered when interpreting our results:

\textbf{Patient selection bias}: The NeuroVista trial included patients with focal epilepsy suitable for implantation, potentially limiting generalizability to other epilepsy types. The requirement for >10 lead seizures during the training period may select for patients with more predictable seizure patterns.

\textbf{Electrode coverage}: The 16-channel arrays provide limited spatial sampling compared to high-density recordings. PAC patterns in regions distant from electrodes may be missed, potentially explaining performance variability across patients.

\textbf{Stationarity assumptions}: Our analysis assumes relative stationarity of PAC patterns over the recording period. However, factors such as medication changes, sleep deprivation, or device-tissue interface evolution could introduce non-stationarities affecting long-term performance.

\textbf{Multiple comparisons}: Despite Bonferroni correction, the analysis of multiple frequency band pairs and time windows increases false discovery risk. Future studies should consider false discovery rate (FDR) control methods.

\subsection{Comparison with Previous Studies}
Our findings extend previous PAC studies in epilepsy in several ways:

Compared to Edakawa et al. (2016), who reported high-frequency oscillation (HFO) coupling in shorter recordings, our long-term analysis reveals slower dynamics and circadian modulation not observable in brief recordings.

Unlike Amiri et al. (2016), who focused on single seizures, our large-scale analysis (>1,500 seizures) provides statistical power to identify consistent patterns and account for seizure-to-seizure variability.

Our improvement over traditional features (+XX\% AUC vs spectral power) is consistent with Jacobs et al. (2018), though our continuous monitoring approach offers advantages for real-world implementation.

\subsection{Future Directions}

Several avenues warrant further investigation:

\textbf{Adaptive algorithms}: Implementing online learning to adapt to non-stationary dynamics and improve long-term stability.

\textbf{Multi-modal integration}: Combining PAC with other biomarkers (HFOs, connectivity measures, behavioral sensors) may further improve prediction accuracy.

\textbf{Mechanism-based interventions}: Understanding PAC dynamics could inform closed-loop stimulation protocols that disrupt pre-ictal buildup.

\textbf{Generalization to other epilepsy types}: Extending analysis to generalized epilepsies and pediatric populations.

\textbf{Optimization of electrode placement}: Using PAC maps to guide surgical planning and optimize electrode positioning for monitoring and stimulation.

\subsection{Implications for Seizure Advisory Systems}
The successful pseudo-prospective evaluation demonstrates feasibility for clinical implementation. A PAC-based advisory system could provide:
- Early warnings (XX minutes) for XX\% of seizures
- Low false positive rates (XX per day) minimizing alarm fatigue
- Personalized risk assessments based on individual PAC patterns

Integration with existing seizure detection algorithms and consideration of circadian patterns could further enhance performance.

\subsection{Conclusion}
This comprehensive analysis of phase-amplitude coupling in long-term iEEG recordings provides robust evidence for PAC as a biomarker of seizure susceptibility. The progressive enhancement of theta-gamma coupling during pre-ictal periods offers both mechanistic insights and practical applications for seizure prediction. Our optimized computational pipeline and systematic database management approach enable scalable analysis applicable to next-generation implantable devices. While patient-specific variability remains a challenge, the consistent patterns across multiple seizures and patients support the clinical translation of PAC-based seizure forecasting systems. Future work should focus on real-time implementation, algorithm adaptation, and integration with therapeutic interventions to improve quality of life for patients with drug-resistant epilepsy.

\label{sec:discussion}
%%%% EOF