%% Response to reviewer 1 comment 1
\subsection*{Response to Reviewer 1, Comment 1}

\authorText{We thank the reviewer for this important point. We have added a comprehensive ``Compilation Performance Benchmarks'' subsection to the Supplementary Results that directly addresses this concern.}

\authorText{Our benchmarking revealed that container startup overhead adds approximately 2 seconds to each compilation cycle on our reference system (16 GB RAM, 8 cores). For a typical manuscript, total compilation time is 12 seconds for initial builds and 4 seconds for incremental builds. While this represents a measurable overhead compared to native LaTeX compilation, we argue that this cost is negligible in the context of typical writing workflows where authors compile documents infrequently (every few minutes at most).}

\authorText{More importantly, the reproducibility benefits become evident when considering the time lost to debugging environment-specific compilation failures in collaborative settings. Our own experience and informal surveys of colleagues suggest that researchers commonly spend 30-60 minutes resolving package version conflicts when collaborating across different systems. The 2-second container overhead is trivial compared to these multi-hour debugging sessions.}

\authorText{We have added this cost-benefit analysis to the Discussion section to help readers understand that while containerization introduces measurable overhead, the reproducibility benefits provide substantial time savings in collaborative workflows. We appreciate the reviewer prompting us to make this trade-off explicit.}
