%% -*- coding: utf-8 -*-

\noindent\hrulefill

\section*{Conclusion}

We sincerely appreciate the time and expertise that the Editor and Reviewers devoted to evaluating our manuscript. Their insightful comments have led to substantial improvements in both the technical documentation and the clarity of our presentation. The revision process has strengthened the manuscript's contribution by prompting us to provide additional validation results, clarify implementation details, and better articulate the framework's advantages for collaborative scientific writing.

All concerns raised during the initial review have been addressed through revisions to the manuscript text, addition of supplementary materials, and clarification of technical specifications. We believe the revised manuscript now provides researchers with a clear understanding of how SciTeX Writer can streamline their manuscript preparation workflow while ensuring reproducibility across diverse computing environments.

Appropriately, this revision letter itself was generated using the SciTeX Writer framework, demonstrating the system's practical utility for managing the peer review process. The structured organization of reviewer comments and author responses, combined with automatic generation of marked-up manuscripts, exemplifies the workflow efficiencies that the framework provides.

We look forward to your decision on the revised manuscript and remain available to address any additional questions or concerns.

Sincerely,

The SciTeX Writer Development Team

%%%% EOF
